---
title: "DataDiveIntroduction"
author: "BjoernBoening"
date: "8. Oktober 2015"
output:
  ioslides_presentation:
    fig_caption: yes
    fig_height: 6
    fig_width: 7
    logo: logo.png
  beamer_presentation: default
---
```{r, include=FALSE}
### Load CSV file
data <- read.csv("E:/bjoer/Documents/Google Drive/Data Animals/Jambo Bukoba/Data/Final data/Final Data.csv")


```
## Test Statistik

```{r echo=FALSE}
names(data) 

```


## The DataAnimals

Welcome to the Berlin Data Dive. 

In the next slides you will learn something about the dataset we have generated. For further questions, feel free to approach one of the present animals at all time or contact us in the web at <http://data-animals.eu>. If you liked our work you can stay in touch with us as well on facebook <http://facebook.com/dataanimals>.


## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}
summary(cars)
```

## Slide with Plot

```{r echo=FALSE}
plot(cars)
```

## Jambo Bukoba slide one - PieChart of students reached in 2014 by gender (just for testing) (CC)


## test
two plus two equals `r 2 + 2`
